\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{top=0.5in, bottom=0.5in, left=0.5in, right=0.5in}
\usepackage{enumitem}
\setlist[itemize]{nosep, left=0pt}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{bold-extra}

\renewcommand{\rmdefault}{ptm} % Times New Roman
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}

% Section title format with a horizontal rule underneath
\titleformat{\section}{\bfseries\large}{}{0em}{}[\titlerule]

\begin{document}

% -------------------- Header --------------------
\begin{center}
    {\LARGE \textbf{Diego Cicotoste}}\\[0.5em]
    \small \href{tel:305-988-8058}{305-988-8058} \textbar{} 
    \href{mailto:cicotosted@gmail.com}{cicotosted@gmail.com} \textbar{} 
    \href{https://www.diegocico.com}{diegocico.com} \textbar{} 
    \href{https://www.linkedin.com/in/diego-cicotoste/}{linkedin.com/in/diego-cicotoste/}
\end{center}

% -------------------- Education --------------------
\section*{Education}
\textbf{Northeastern University}, Boston, MA \hfill Sept 2023 -- Jun 2026\\
B.S. in Computer Science \hfill \textit{Study Abroad: London}

% -------------------- Experience --------------------
\section*{Experience}
\textbf{Amazon} \hfill \textit{Software Development Engineering Intern (Incoming)}\\
May 2025 -- Aug 2025\\[0.5em]

\textbf{Supply Trace} \hfill \textit{Data Engineer / Project Manager}\\
Sept 2024 -- Present
\begin{itemize}
    \item Led a high-performance team of 12, ensuring timely completion of tasks.
    \item Developed efficient algorithms to process and merge millions of data points monthly.
    \item Assisted in rebuilding infrastructure for faster, safer data loading.
\end{itemize}

\textbf{Amazon} \hfill \textit{Software Development Engineering Intern}\\
May 2024 -- Aug 2024
\begin{itemize}
    \item Processed data from over 2 million users via the Productiv API to enhance business insights.
    \item Designed and deployed a TypeScript data pipeline, cutting processing time by 40\%.
    \item Implemented data visualization on Amazon QuickSight, contributing to a \$10M cost reduction.
\end{itemize}

\textbf{Code Ninjas Aventura} \hfill \textit{Manager}\\
Jun 2021 -- Aug 2023
\begin{itemize}
    \item Supervised 15 instructors, managing operations, scheduling, and training.
    \item Generated \$30K+ monthly revenue, peaking at over \$70K during summer camps.
\end{itemize}

% -------------------- Projects --------------------
\section*{Projects}
\begin{itemize}
    \item \textbf{DYA}: Developed a full back-end using Firebase and JavaScript with integrated front-end support.
    \item \textbf{AlgoVisualizer}: Created a Python application that interactively visualizes sorting algorithms.
    \item \textbf{Predator and Prey Sim}: Built a Java simulation modeling dynamic interactions in an ecosystem.
    \item \textbf{HouseFinder}: Developed a Python application on AWS EC2/S3 to track house listings, analyze prices, and generate weekly CSV reports with charts.
\end{itemize}

% -------------------- Community Involvement --------------------
\section*{Community Involvement}
\textbf{AFE Ambassador} \hfill \textit{Jan 2025 -- Present}\\
Represent Amazon on student panels and organize events for the AFE Scholarship program.\\[0.5em]

\textbf{MMBank} \hfill \textit{Web Developer}\\
Nov 2024 -- Jan 2025\\
Designed and developed an engaging website for a leading bank in Brazil.\\[0.5em]

\textbf{The Hope Box Club} \hfill \textit{Founder}\\
Jun 2021 -- May 2023\\
Founded a club dedicated to collecting toys and essential items for underprivileged children (target: 1,500 boxes/year).

% -------------------- Skills --------------------
\section*{Skills}
\textbf{Technical:} Android Studio, IntelliJ, Flutter, VSCode, NetBeans, Xcode, PyCharm, AWS Console, Firebase, REST\\[0.5em]
\textbf{Languages:} Java, Kotlin, C\#, Python, Dart, HTML, CSS, Swift, TypeScript, MySQL, JavaScript, C++, React.js\\[0.5em]
\textbf{Interests:} Snowboarding, Hackathons, Gym, Personal Projects, Hiking, Traveling, Networking

\end{document}
